---
title: "IBM Customer Behavior Analysis"
output: word_document
date: "2022-11-15"
---

```{r}
install.packages("dplyr")
install.packages("ggplot2")
install.packages("reshape2")
library(dplyr)
library(ggplot2)
library(reshape2)
```

```{r}

df <- read.csv("C:/Users/Aishat/Downloads/WA_Fn-UseC_-Marketing-Customer-Value-Analysis.csv/WA_Fn-UseC_-Marketing-Customer-Value-Analysis.csv")
head(df)

```

```{r}

is.data.frame(df)

```

```{r}
dim(df)
```


```{r}

str(df)

```

```{r}

colnames(df)

```
# Data Cleaning
```{r}
colSums(sapply(df, is.na))
```

```{r}
any(is.na(df))
```

```{r}
df$State <- as.factor(df$State)
is.factor(df$State)
df$Coverage <- as.factor(df$Coverage)
is.factor(df$Coverage)
df$Education<- as.factor(df$Education)
is.factor(df$Education)
```
```{r}
str(df)
```

```{r}
head(df)
```

# ANALYSIS
# Encode conversions (default) as 0 and 1 (instead of "Yes" and "No")
```{r}

df <- df %>%
  mutate(Response = ifelse(Response == "No", 0, 1))
df$Response <- as.integer(df$Response)
head(df)

```
# To calculate the Conversion/Engagement Rate
```{r}

EngagementRate <- df %>%
  group_by(Response) %>%
  summarize(Count=n()) %>%
  mutate(Percentage=Count/nrow(df)*100)

#transpose 
transposed <- t(EngagementRate)
colnames(transposed) <- EngagementRate$Response
transposed <- transposed[-1,]
transposed

```

# To Take a look at the Response rates by the different sales channels. 
```{r}

SalesChannel <- df %>%
  group_by(Response, Sales.Channel) %>%
  summarize(Count=n()) %>%
  arrange(Sales.Channel)

options(repr.plot.width = 20, repr.plot.height = 10)
ggplot(SalesChannel, aes(x="", y=Count, fill=Sales.Channel)) +
  geom_bar(stat = "identity", position = position_fill()) +
  geom_text(aes(x=1.0, label=Count), position = position_fill(vjust=0.5)) +
  coord_polar("y") + facet_wrap(~Response) +
  ggtitle("Sales Channel (No, Yes)") + 
  theme(legend.position = "right", legend.text=element_text(size=20), plot.title = element_text(size=22))

```
# Customer Conversion Rates by the States.
```{r}

conversionsState <- df %>%
  group_by(State) %>%
  summarize(TotalCount=n(), NumConversions=sum(Response)) %>%
  mutate(ConversionRate=NumConversions/TotalCount*100)
conversionsState

```


# Getting the numeric columns from the dataset
```{r}

numeric1 <-select_if(df, is.numeric)
numeric1
cor(numeric1)

```

# Plotting Scatterplot for numerical value
```{r}

pairs(numeric1)
plot(numeric1, main ="Scatterplot matrix")

```

# Summary of Numerical features
```{r}

summary(numeric1)

```

```{r}

library(corrplot)
corrplot(cor(numeric1),
         type = "full",
         diag = TRUE,
         tl.col = "black",
         bg = "white",
         title = "",
         col = NULL)

```

## Total.Claim.Amount seems to be correlated with Monthly.Premium.Auto, Income and Customer.Lifetime.Value. So I will investigate further


```{r}

plot(df$Total.Claim.Amount, df$Monthly.Premium.Auto, main ="Total Claim Amount Vs Monthly Premium Auto", xlab = "Monthly Premium", ylab = " Total Claim",  col = "steelblue")

```


```{r}

plot(df$Monthly.Premium.Auto, df$Customer.Lifetime.Value, main ="Customer Lifetime Value Vs Monthly Premium Auto", xlab = "Monthly Premium", ylab = "Customer Lifetime Value", col = "red")

```


```{r}

plot(df$Total.Claim.Amount, df$Income, main ="Total Claim Amount Vs Income", xlab = "Income", ylab = "Total Claim", col = "blue")

```


```{r}

plot(df$Total.Claim.Amount, df$Customer.Lifetime.Value, main ="Total Claim Amount Vs Customer Lifetime Value",xlab = "Customer Lifetime Value", ylab = "Total Claim", col = "purple")

```


```{r}

summary(df)

```


# Effect of Employment Status on Customer Time Value
```{r}
boxplot(Customer.Lifetime.Value ~ EmploymentStatus, df,                               
        main = "Visualization of Customer Lifetime Value Vs Employment Status",
        xlab = "EmploymentStatus",
        ylab = "Customer.Lifetime.Value",
        col = "blue")

```
# Effect of Location on Customer Life Time Value
```{r}
boxplot(Customer.Lifetime.Value ~ Location.Code, df,                               
        main = "Visualization of Customer Lifetime Value Vs Location Code",
        xlab = "Location.Code",
        ylab = "Customer.Lifetime.Value",
        col = "steelblue")

```


```{r}
heatmap(cor(numeric1))
```





# ANALYSIS OF CONTINOUS VARIABLES WITH CATEGORICAL VARIABLES

```{r}
lg1 <- lm(df$Total.Claim.Amount ~ df$State)
summary(lg1)
```

```{r}
df1<-aggregate(x = df$Total.Claim.Amount,                
                    by = list(df$State),             
                    FUN = sum)
df1
piepercent3<- round(100 * df1$x / sum(df1$x), 1)
pie(df1$x, labels =piepercent3,
    main = "Total Claim Amount by State",col = rainbow(length(df1$x)))
legend("topright", c("Arizona", "Califonia", "Nevada","Oregon","Washington"),
       cex = 0.65, fill = rainbow(length(df1$x)))


```


```{r}
lg2 <- lm(df$Total.Claim.Amount ~ df$Education)
summary(lg2)
```

```{r}
df2 <-aggregate(x = df$Total.Claim.Amount,                
                    by = list(df$Education),              
                    FUN = sum)
df2
piepercent4<- round(100 * df2$x / sum(df2$x), 1)
pie(df2$x, labels =piepercent4,
    main = "Total Claim Amount Vs Education",col = rainbow(length(df2$x)))
legend("topright", c("Bachelor", "College", "Doctor","High Sch or Below","Master"),
       cex = 0.65, fill = rainbow(length(df2$x)))
```


```{r}
lg3 <- lm(df$Total.Claim.Amount ~ df$Coverage)
summary(lg3)
```

```{r}

df3 <- aggregate(x = df$Total.Claim.Amount, by = list(df$Coverage), FUN = sum)
piepercent1 <- round(100 * df3$x / sum(df3$x), 1) 
pie(df3$x, labels =piepercent1,
    main = "Total Claim Amount by Coverage",col = rainbow(length(df3$x)))
legend("topright", c("Basic", "Extended", "Premium"), 
       cex = 0.8, fill = rainbow(length(df3$x)))

```

# Contigency tables for categorical Variables

```{r}
cont.table1 <- table(df$Coverage, df$Education)
cont.table1
```


```{r}
ggplot(df, aes(x=Coverage, y=Education, fill=Total.Claim.Amount)) + geom_tile()
```


```{r}
cs.1 <- chisq.test(cont.table1)
cs.1
```

#Multiple Linear Regression

```{r}
model1 <- lm(Total.Claim.Amount ~ Monthly.Premium.Auto + Coverage + Education, data = df)
anova(model1); summary(model1)
```

```{r}
model2 <- lm(Total.Claim.Amount ~ Income + Monthly.Premium.Auto + Education + Coverage, data = df)
anova(model2); summary(model2)
```

```{r}
model3 <- lm(Total.Claim.Amount ~ Customer.Lifetime.Value + Education + Coverage, data = df)
anova(model3); summary(model3)
```


```{r}
model4 <- lm(Total.Claim.Amount ~ Monthly.Premium.Auto + Income + Customer.Lifetime.Value + Education + Coverage, data = df)
anova(model4); summary(model4)
```

```{r}
model5 <- lm(Total.Claim.Amount ~ Income + Monthly.Premium.Auto + Customer.Lifetime.Value + Response + Education + Coverage, data = df)
anova(model5); summary(model5)
```


```{r}
confint(model5)
```


```{r}
plot(lm(Total.Claim.Amount ~ Income + Monthly.Premium.Auto + Customer.Lifetime.Value + Response + Education + Coverage, data = df))
```

```{r}
plot(rstudent(model5))
```


```{r}
library(MASS)

```


```{r}
set.seed(55)
cluster.df <- kmeans(df[, 22, 6], 3, nstart = 20)
cluster.df
```


```{r}
table(cluster.df$cluster, df$Education)
````

```{r}
cluster.df$cluster <- as.factor(cluster.df$cluster)
```

```{r}

ggplot(df, aes(Education, Total.Claim.Amount, color = cluster.df$cluster)) + geom_point() + ggtitle("Cluster of Education and Total Claim Amount")

```


```{r}

```


```{r}

````


```{r}

```


```{r}

```


```{r}

````
